### 2022-08-23 manuscript.Rmd
Fix citations

```{r, setup, include=FALSE}
# Load R packages
library(buildmer)
library(emmeans)
library(here)
library(knitr)
library(lmerTest)
library(MASS)
library(scales)
library(papaja)
library(cowplot)
library(parallel)
library(reticulate)
library(tidyverse)
library(magrittr)

@@

The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different aspects of cognition from early on [@churchland1994; @lupyan2015].
This view is supported by a variety of theoretical, behavioral, and neurophysiological accounts.
On the theoretical level, the reverse hierarchy theory [@ahissar2004; @hochstein2002] posits that conscious processing initally occurs at the level of whole objects or object categories.
Only after this high-level interpretation has been obtained, more fine grained visual details---if relevant for the current task---are being accessed via top-down connections.
Along similar lines, Bayesian inference and predictive coding theories [e.g., @clark2013; @panichello2013; @yuille2006] propose bi-directional loops of predictions and prediction errors between visual and non-visual processes.

>>>>

```{r, setup, include=FALSE}
# Load R packages
library(buildmer)
library(emmeans)
library(here)
library(knitr)
library(lmerTest)
library(MASS)
library(scales)
library(papaja)
library(eegUtils)
library(cowplot)
library(parallel)
library(reticulate)
library(tidyverse)
library(magrittr)

@@

The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different aspects of cognition from early on [@churchland1994; @lupyan2015].
This view is supported by a variety of theoretical, behavioral, and neurophysiological accounts.
On the theoretical level, the reverse hierarchy theory [@ahissar2004; @hochstein2002] posits that conscious processing initally occurs at the level of whole objects or object categories.
Only after this high-level interpretation has been obtained, more fine grained visual details---if relevant for the current task---are being accessed via top-down connections.
Along similar lines, Bayesian inference and predictive coding theories [e.g., @yuille2006; @clark2013; @panichello2013] propose bi-directional loops of predictions and prediction errors between visual and non-visual processes.
